---
title: "FANOVA Example Burn-In"
author: "Jon Hobbs"
date: "May 15, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MIP North America Example Functional ANOVA

### 

Burn-in diagnostics for functional ANOVA MCMC run, OCO-2 V9 MIP over North America  
Response is posterior-prior

* Factor A: Model
* Factor B: Data Source (IS, LNLG)

```{r source_lib, include=FALSE}
library(fields)
library(ncdf4)
library(ggplot2)
```

```{r local_lib, results='hide'}
source("func_anova_tidy.R")

theme_mat = theme_bw() 
theme_mat$strip.text$size = 12
theme_mat$axis.title.x$size = 12
theme_mat$axis.text.x$size = 11
theme_mat$axis.title.y$size = 12
theme_mat$axis.text.y$size = 11
theme_mat$plot.title$size = 12
theme_mat$plot.title$hjust = 0.5
theme_mat$legend.text$size = 10
theme_mat$legend.title$size = 10
```

```{r read_config, results="hide"}
exmpcfg = read.csv("config/fanova_mip_namer_prdev_sptm.csv",header = TRUE,stringsAsFactors = FALSE)
cfglst = as.list(exmpcfg$Value)
names(cfglst) = exmpcfg$Field
```

### GP Parameters

Trace plots for Gaussian process parameters

```{r gp_traces, results="hide"}
gpgrps = c("mean","mainA","mainB","interact","noise")
gpbnms = paste0(cfglst$output_dir,"/mip_sp_pars_",gpgrps,"_burn.png")
gprfrm = data.frame(vrnm=gpgrps,ofile=gpbnms,nrow=rep(2,5),width=rep(1200,5),height=rep(900,5),
                    arparam=c(rep(FALSE,4),TRUE),stringsAsFactors = FALSE)
for (i in seq(1,nrow(gprfrm))) {
    gp_partrace_burn(gprfrm[i,],cflst=cfglst,pltthm=theme_mat,nstrt=151)
}
```

```{r gp_show_trace, results='asis', echo = FALSE}
for (i in seq(1,nrow(gprfrm))) {
    cat("![", gprfrm$vrnm[i], "](", gprfrm$ofile[i], ")\n")  
}
```

### MH Acceptance

Metropolis-Hastings acceptance rates

```{r gp_mh, results="hide"}
mhfrm = gprfrm
mhfrm$width=rep(750,5)
mhfrm$height=rep(600,5)
mhfrm$ofile = paste0(cfglst$output_dir,"/mip_mh_sp_pars_",gpgrps,"_burn.png")
for (i in seq(1,nrow(gprfrm))) {
    ascatter(mhfrm[i,],cflst=cfglst,pltthm=theme_mat)
}
```

```{r gp_mh_show_trace, results='asis', echo = FALSE}
for (i in seq(1,nrow(mhfrm))) {
    cat("![", mhfrm$vrnm[i], "](", mhfrm$ofile[i], ")\n")  
}
```

### ANOVA fields at selected locations

Trace plots for the ANOVA elements at selected locations

```{r gp_field_mean, results="hide"}
nctra = as.integer(cfglst$nleva) - 1
nctrb = as.integer(cfglst$nlevb) - 1
nctri = nctra * nctrb
fldfrm = gprfrm[1:4,]
fldfrm$nctrst = c(0,nctra,nctrb,nctri)
fldfrm$locst = rep(2,4)
fldfrm$locfn = rep(98,4)
fldfrm$locinc = rep(12,4)
fldfrm$nrow = rep(3,4)
fldfrm$ndigit = rep(1,4)
fldfrm$height[fldfrm$nctrst > 1] = 1800
fldfrm$width[fldfrm$nctrst > 1] = fldfrm$nctrst[fldfrm$nctrst > 1] * 250
fldfrm$ofile = paste0(cfglst$output_dir,"/mip_field_locs_",gpgrps[1:4],"_burn.png")
for (i in seq(1,nrow(fldfrm))) {
    gp_fldtrace_burn(fldfrm[i,],cflst=cfglst,pltthm=theme_mat,nstrt=151)
}
```

```{r gp_field_show_trace, results='asis', echo = FALSE}
for (i in seq(1,nrow(fldfrm))) {
    cat("![", fldfrm$vrnm[i], "](", fldfrm$ofile[i], ")\n")  
}
```

***

### Further MH diagnostics

Covariance of spatial params, by chain

Mean

```{r gp_cov_mean}
chsq = seq(1,cfglst$nchain)
gpgrps = c("mean","mainA","mainB","interact","noise")
vnms = c("LogSD","LogRg","LogitNu")
numn = 0.25
numx = 3.75
gcvsmn = gp_parcov_burn(vrnm="mean",cflst=cfglst,nstrt=151)

# Adjust for logit
gcvsmn[,3,] = exp(gcvsmn[,3,])
nustr = (gcvsmn[,3,]-numn) / (numx-numn)
gcvsmn[,3,] = log(nustr/(1.0-nustr))

# Summarize
cvchnmn = apply(gcvsmn,3,cov)
frmmn = map_dfr(chsq, .f=covs_frm, cvmt=cvchnmn, vrnms=vnms)
print(frmmn)
```

Main A

```{r gp_cov_mainA}
gcvsa = gp_parcov_burn(vrnm="mainA",cflst=cfglst,nstrt=151)
# Adjust for logit
gcvsa[,3,] = exp(gcvsa[,3,])
nustr = (gcvsa[,3,]-numn) / (numx-numn)
gcvsa[,3,] = log(nustr/(1.0-nustr))

# Summarize
cvchna = apply(gcvsa,3,cov)
frma = map_dfr(chsq, .f=covs_frm, cvmt=cvchna, vrnms=vnms)
print(frma)
```

Main B

```{r gp_cov_mainB}
gcvsb = gp_parcov_burn(vrnm="mainB",cflst=cfglst,nstrt=151)
# Adjust for logit
gcvsb[,3,] = exp(gcvsb[,3,])
nustr = (gcvsb[,3,]-numn) / (numx-numn)
gcvsb[,3,] = log(nustr/(1.0-nustr))

# Summarize
cvchnb = apply(gcvsb,3,cov)
frmb = map_dfr(chsq, .f=covs_frm, cvmt=cvchnb, vrnms=vnms)
print(frmb)
```

Interact

```{r gp_cov_interact}
gcvsi = gp_parcov_burn(vrnm="interact",cflst=cfglst,nstrt=151)
# Adjust for logit
gcvsi[,3,] = exp(gcvsi[,3,])
nustr = (gcvsi[,3,]-numn) / (numx-numn)
gcvsi[,3,] = log(nustr/(1.0-nustr))

# Summarize
cvchni = apply(gcvsi,3,cov)
frmni = map_dfr(chsq, .f=covs_frm, cvmt=cvchni, vrnms=vnms)
print(frmni)
```

Noise

```{r gp_cov_noise}
vnms = c("LogSD","LogRg","LogitNu","LogitRho")
gcvsns = gp_parcov_burn(vrnm="noise",cflst=cfglst,nstrt=151,logpar=FALSE,arparam=TRUE)
# Adjust for logit
gcvsns[,1,] = log(gcvsns[,1,])
gcvsns[,2,] = log(gcvsns[,2,])

nustr = (gcvsns[,3,]-numn) / (numx-numn)
gcvsns[,3,] = log(nustr/(1.0-nustr))

rhomn = -1.0
rhomx = 1.0
nustr = (gcvsns[,4,]-rhomn) / (rhomx-rhomn)
gcvsns[,4,] = log(nustr/(1.0-nustr))

# Summarize
cvchnns = apply(gcvsns,3,cov)
frmns = map_dfr(chsq, .f=covs_frm, cvmt=cvchnns, vrnms=vnms)
print(frmns)
```
